decompr: GVC decomposition in R

### 2015-01-29 draft.Rnw
Update draft.Rnw

\section{Data}
\label{sec:data}
Two data sets are included in the package, one real world data set, and one minimal fictional data for training purposes.
The former is the WIOD regional Inter-Country Input Output table for the year 2011 \parencite{timmer2012world}. 
The latter is a fictional 3-country 3-sector data set is included, which we will use throughout this article to exemplify
the mechanics of the package.

>>>>

\section{Data}
\label{sec:data}
Two data sets are included in the package, one real world data set, and one minimal fictional data for training purposes.
The former is the WIOD regional Inter-Country Input Output table for the year 2011 \parencite{timmer2012world}. 
The latter is a fictional 3-country 3-sector data set, which we will use throughout this article to exemplify
the mechanics of the package. The data can be accessed as follows:
